---
title: ggdirect
subtitle: ""
author: "Exploded Examples"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, echo = F}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, fig.height = 6, comment = "")
options(knitr.duplicate.label = "allow")
library(ggdirect)
```


---

`r flipbookr::chunk_reveal('geom_bubble_1', title = '### geom_bubble')`

```{r geom_bubble_1, include = F}
# using function
library(ggplot2)
ggplot(cars) +
  aes(x = speed, y = dist) +
  geom_bubble(size = 7,
    alpha = .85,
    color = "white",
    fill = "plum2"
   ) +
 theme_minimal()
```



---

`r flipbookr::chunk_reveal('geom_bubble_2', title = '### geom_bubble')`

```{r geom_bubble_2, include = F}
# without function
library(ggplot2)
ggplot(cars) +
  aes(x = speed, y = dist) +
  geom_point(shape = 21,size = 7,
    alpha = .85,
    color = "white",
    fill = "plum2")
 geom_bubble
```



---

`r flipbookr::chunk_reveal('geom_line_endpoint_3', title = '### geom_line_endpoint')`

```{r geom_line_endpoint_3, include = F}
# functions
ggdirect:::StatLineendpoint
geom_line_endpoint
library(ggplot2)
ggplot(cars) +
   aes(x = speed, y = dist) +
   geom_line() +
   geom_line_endpoint()
ggplot(cars) +
    aes(x = speed, y = dist, color = dist > 15) +
    geom_line() +
    geom_line_endpoint()
ggplot(cars) +
     aes(x = speed, y = dist,
         color = dist > 15,
         linetype = speed > 16) +
     geom_line() +
     geom_line_endpoint()
```



---

`r flipbookr::chunk_reveal('geom_ring_4', title = '### geom_ring')`

```{r geom_ring_4, include = F}
# using function
library(ggplot2)
ggplot(cars) +
  aes(x = speed, y = dist) +
  geom_ring(size = 7, color = "slateblue")
```



---

`r flipbookr::chunk_reveal('geom_ring_5', title = '### geom_ring')`

```{r geom_ring_5, include = F}
# without function
library(ggplot2)
ggplot(cars) +
  aes(x = speed, y = dist) +
  geom_ring(size = 7, color = "slateblue")
 geom_ring
```



---

`r flipbookr::chunk_reveal('text_count_percentage_6', title = '### text_count_percentage')`

```{r text_count_percentage_6, include = F}
library(ggplot2)
ggplot(mtcars) +
    aes(x = cyl) +
    geom_bar() +
    geom_text_count_percent(nudge_y = .5)
```



---

`r flipbookr::chunk_reveal('text_count_7', title = '### text_count')`

```{r text_count_7, include = F}
library(ggplot2)
ggplot(mtcars) +
   aes(x = cyl) +
   geom_bar() +
   geom_text_count(nudge_y = .5)
```


